GUI Testing as a Service

### 2016-03-31 doc/paper/james/2016_ASE_ChengLin/paper.tex
fix bug remove database from catg

The GUI shown in Figure~\ref{fig:ex} is an application that we developed to mimic the motivating example used in Barad~\cite{}. calculate the price for a train ticket. The application calculates the price for a train ticket based on the information passed through the GUI. A user must provide a passenger class, name, ID, age level, and begin
and end points. Each passenger class has its own coefficient that is used during the calculation. Each age level has a different
base price depending on the distance to be traveled,
which is the difference between From mile and To mile. Figure~\ref{fig:code} gives the code snippet of the calculation logic.  There are twenty four branches. The
execution of a particular branch depends on the user
input both in the form of data and event sequence (i.e.
selecting a radio button).

This program is used to calculate ticket price according to different properties of the client, such as the class level, or age, or the travel distance. When the \texttt{Buy} button is clicked, the application check the \texttt{Name} and \texttt{ID} input, if the length of the \texttt{Name} string is less or equal than 3, or \texttt{ID} equals to some special string, then the application will display an error message and will not calculate any price. After checking the user information successfully, the application start to calculate the price as follows: read the user class input and set a coefficient for the price, read the user age to go to different pricing branch, read the start and destination input and calculate the distance of traveling, then calculate the price. We can see from the following code snippets that there should be many branches in the code to calculate ticket price for all kinds of clients.

\begin{figure}
\label{fig:code}
\begin{lstlisting}
OnClickCalculatePrice() {
  int coefficient = (classLevel == TicketModel.FIRSTCLASS) ? 2 : 1;
  int dist = to - from;
  assert(dist>0);
  if (ageLevel == Adult) {
    if (dist < 40) {
      price = 100 * coeficient;
    } else if (dist < 45) {
      price = 110 * coeficient;
    } else if (dist < 50) {
      ...
    } 
    ...  
  }
  else if (ageLevel == Senior) {
      ...
  }
 else if (ageLevel == Student) {
        ...
  }
  else if (ageLevel == Child) {
       ... 
   }      
   Price.Display(price);
}

OnClickClassLevel1st(){
  classLevel = FIRSTCLASS;
}

OnClickBuyTicket(){
  assert(price<=maxPrice&&price>=minPrice);
}

OnClickClear(){
   Name=ID=null;
   From=To=0;
   AgeLevel=Adult;
   FirstClass=True;
   2ndClass=False;
 }
\end{lstlisting}
\caption{Code snippet for calculating ticket price}
\end{figure}

Lin, please do the following
1. The code above is just imagination. Please revise it so that our approach can catch some tricky assertion failures.
2. Please give a step-by-step illustration on how our algorithm detects errors in the example

@@

Lin, please provide algorithm pseudo-code here and give some explanation.

>>>>

The GUI shown in Figure~\ref{fig:ex} is an application that we developed to mimic the motivating example used in Barad~\cite{}. calculate the price for a train ticket. The application calculates the price for a train ticket based on the information passed through the GUI. A user must provide a passenger class, name, ID, age level, and begin
and end points. Each passenger class has its own coefficient that is used during the calculation. Each age level has a different
base price depending on the distance to be traveled,
which is the difference between From mile and To mile. Figure~\ref{fig:code} gives the code snippet of the calculation logic.  There are twenty two branches with conditional statements nested three levels deep. The
execution of a particular branch depends on the user
input both in the form of data and event sequence (i.e.
selecting a radio button).

This program is used to calculate ticket price according to different properties of the client, such as the class level, or age, or the travel distance. When the \texttt{Buy} button is clicked, the application check the \texttt{Name} and \texttt{ID} input, if the length of the \texttt{Name} string is less or equal than 3, or \texttt{ID} equals to some special string, then the application will display an error message and will not calculate any price. After checking the user information successfully, the application start to calculate the price as follows: read the user class input and set a coefficient for the price, read the user age to go to different pricing branch, read the start and dest input and calculate the distance of travelling, then calculate the price. We can see from the following code snippets that there should be many branches in the code to calculate ticket price for all kinds of clients.
\begin{figure}
\label{fig:code}
\begin{lstlisting}
  int maxPrice = 100;
  int minPrice = 10;
  int coefficient = (classLevel == TicketModel.FIRSTCLASS) ? 2 : 1;
  int dist = to - from;
  if (ageLevel == Adult) {
    if (dist < 40) {
      price = 100 * coeficient;
    } else if (dist < 45) {
      price = 110 * coeficient;
    } else if (dist < 50) {
      price = 120 * coeficient;
    } else if (dist < 70) {
      price = 140 * coeficient;
    } else if (dist < 80) {
      price = 150 * coeficient;
    } else if (dist < 85) {
      price = 155 * coeficient;
    } else if (dist < 100) {
      price = 160 * coeficient;
    }
  }
  assert(price<=maxPrice&&price>=minPrice);
\end{lstlisting}
\caption{Code snippet for calculating ticket price}
\end{figure}

One can not claim this kind of applications are well tested until all the branches has been covered during test stage.

@@
